Collapsed Cores in Globular Clusters, \\ Gauge-Boson Couplings, and AAS\TeX\ Examples

### 2014-01-17 tex/paper1/paper1.tex
more on paper, more output from main analysis code

A focal problem today in the dynamics of globular clusters is core collapse.  
It has been predicted by theory for decades \citep{hen61,lyn68,spi85}, but
observation has been less alert to the phenomenon. For many years the
central brightness peak in M15 \citep{kin75,new78} seemed a unique anomaly.  
Then \citet{aur82} suggested a central peak in \object{NGC 6397}, and a 
limited photographic survey of ours \citep[Paper I]{djo84} found three more 
cases, \objectname{NGC 6624}, \objectname[M 15]{NGC 7078}, and 
\object[Cl 1938-341]{Terzan 8}), whose sharp center had often been 
remarked on \citep{can78}.

As an example of how the new AASTeX object tagging macros work, we will
cite some of the ``Superlative'' objects mentioned in section 10 of
Trimble's (1992) review of astrophysics in the year 1991.  The youngest
star yet found was \object[\[JCC87\] IRAS 4]{IRAS 4} in \objectname{NGC 1333}.
\object{70 Oph} was found to be the longest period spectroscopic binary.
The most massive white dwarf was \object{GD 50}, estimated at 1.2 solar masses.
The first neutral hydrogen found in a globular cluster was \object{NGC 2808}
while the \objectname[SDSS J093401.92+551427.9]{I Zw 18} retained the
record for metal deficiency.  However, another low metallicitity
galaxy was \object{UGC 4483} in the \objectname{M 83} group. The
largest redshift \object[PC 1247+3406]{source} in 1991 was found at
z=4.897.  Lastly, what paper would be complete without a mention of the
\object[M1]{Crab nebula}!

@@

All our observations were short direct exposures with CCD's.  We also have
a random {\it Chandra} data set \dataset{ADS/Sa.ASCA\#X/86008020} and a
neat \dataset[ADS/Sa.HST#Y0Q70101T]{HST FOS spectrum} that readers can access
via the links in the electronic edition.  Unfortunately this has nothing 
whatsoever to do with this research.  At Lick Observatory we used a TI 500$\times$500 
chip and a GEC 575$\times$385, on the 1-m Nickel reflector.  The only
filter available at Lick was red.  At CTIO we used a GEC 575$\times$385, with
$B, V,$ and $R$ filters, and an RCA 512$\times$320, with $U, B, V, R,$ and $I$
filters, on the 1.5-m reflector. In the CTIO observations we tried to
concentrate on the shortest practicable wavelengths; but faintness, reddening,
and poor short-wavelength sensitivity often kept us from observing in $U$ or
even in $B$. All four cameras had scales of the order of 0.4 arcsec/pixel, and
our field sizes were around 3 arcmin.

The CCD images are unfortunately not always suitable, for very poor
clusters or for clusters with large cores.  Since the latter are easily
studied by other means, we augmented our own CCD profiles by collecting
from the literature a number of star-count profiles 
\citep{kin68,pet76,har84,ort85}, as well as photoelectric profiles 
\citep{kin66,kin75} and electronographic profiles \citep{kro84}.
In a few cases we judged normality by eye estimates on one of the Sky
Surveys.

@@

\section{Results}
\label{sec:results}

@@

>>>>

The solar corona is observed to support many different oscillatory
phenomena.

@@

Data was obtained from SDO-AIA using the Lockheed Martin Solar
Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
hours of image data at 12 second cadence was selected in the 171\AA,
193\AA, 211\AA\ and 131\AA\ wavebands (2012-09-22 00:00 - 06:00 UT,
1800 images per waveband).  These wavebands were selected in order to
obtain a wide range of approximate temperatures in the solar corona.

The downloaded cutout data was prepared for analysis using the
SolarSoft / IDL routines READ\_SDO and AIA\_PREP.  These procedures
move the downloaded level 1.0 FITS files to level 1.5 FITS files.  All
further processing from this point was performed in the SunPy 0.4
(http://www.sunpy.org) data analysis environment.

Datacubes were formed in each waveband.  The data were
de-rotated using fractional pixel offsets relative to the first image
in the data, with the amount of offset calculated based on solar
rotation (Howard et
al. http://adsabs.harvard.edu/abs/1990SoPh..130..295H).

\section{Analysis}

@@

\section{Results}
\label{sec:results}
Figure \ref{}

@@

Section \ref{sec:results} demonstrates the presence of a red
noise-like signal in two of the most commonly used wavebands for
coronal seismology, SDO-AIA 171\AA\ and 193\AA.
